Dependent Object Types

### 2012-08-30 doc/candidacy/report.tex
intro

@@

I present three papers~\cite{nuObj,tribe,homl}, each of which models a
calculus with path-dependent types.

>>>>

% TODO intro

\IEEEPARstart{T}{he} aim of this research is to propose a new sound
and tractable type-theoretic foundation of Scala and languages like
it: the Dependent Object Types calculus (DOT). The properties we are
interested in modeling are Scala's path-dependent types and abstract
type members, as well as its mixture of nominal and structural typing
through the use of refinement types. Compared to previous
approaches~\cite{nuObj,FS}, we make no attempt to model inheritance or
mixing composition. Furthermore, the calculus is more normative than
descriptive, in that it does not precisely describe what's currently
in Scala.

Path-dependent types are a key concept in the DOT calculus, and a
unifying concept of the three papers we choose to study. A {\it
  dependent type} is a type which depends on a term. A {\it
  path-dependent type} is a limited form of dependent type, in which a
type depends on a path: a chain of immutable fields or
variables. Path-dependent types arise when terms, usually objects, can
have types as members.

@@

We present three papers~\cite{nuObj,tribe,homl}, each of which models a
calculus with path-dependent types.
